Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-12 manuscript/manuscript.tex
Improve exponential density text

For an exponential density function, the density-based discretization will be applied
before the adaptive discretization algorithm.
This means that optimal values for both the distance-size ratio $D$ and the delta ratio
$\delta$ must be determined.
We perform an error analysis similar to what was done for the linear density case.
However, we only consider the ``Big Grid'' from Table \ref{tab:grids} for the
sake of brevity.

The spherical shell and tesseroid model will have an exponential density function given
by

\begin{equation}
    \rho(r') = A e^{-(r' - R)/b} + C,
\label{eq:density-exp}
\end{equation}

@@

\begin{equation}
    A =
    (3300 \text{kg/m}^3 - 2670 \text{kg/m}^3)
    \left( e^{( R - R_1 )/b} - 1 \right)^{-1},
\end{equation}

\begin{equation}
    C =
    2670 \text{kg/m}^3 - A,
\end{equation}

\noindent $R$ is the mean Earth radius, $R_1$ is the inner radius of the
shell (determined by the thickness), and $b$ is a constant that determines the
variability of the function: a low value of $b$ increases the maximum slope of the
density function.

@@

Moreover, an exponential density function that assumes the values of $\rho_\text{out}$
and $\rho_\text{in}$ on the shell's outer and inner surfaces, respectively, can be
defined as follows:

The analytical solution of the gravitational potential generated by a
spherical shell with such density function is

\begin{equation}
    \begin{split}
        V_\text{exp}(r) = & \frac{4\pi G}{r} \frac{A T^3}{b^3} \\ \Big[
        & \left( \left( b R_1/T \right)^2 + 2 b R_1/T + 2 \right)
        e^{- \frac{b}{T} (R_1 - R)} - \\
        & \left( \left( b R_2/T \right)^2 + 2 b R_2/T + 2 \right)
        e^{- \frac{b}{T} (R_2 - R)}
        \Big] + \\
        & \frac{4\pi G}{3 r} C \left( R_2^3 - R_1^3 \right).
    \end{split}
\label{eq:shell-pot-exp}
\end{equation}

>>>>

For an exponential density function, the density-based discretization will be applied
before the adaptive discretization algorithm.
This means that optimal values for both the distance-size ratio $D$ and the delta ratio
$\delta$ must be determined.
We perform an error analysis similar to what was done for the linear density case.
But, now the spherical shell will have an exponential density function that assumes the
values of $\rho_\text{out} = 2670$~kg/m$^3$ and $\rho_\text{in} = 3300$~kg/m$^3$ on the
outer and inner surfaces, respectively, defined as follows:
by

@@

@@
